%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

%\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\usepackage{hyperref}

\name{Woo Seok Jung} % Your name
\address{6656 Walnut Street \\ Cypress, California 90630} % Your address
\address{(562)~$\cdot$~760~$\cdot$~8825 \\ wjung@pugetsound.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Puget Sound}, Tacoma, WA \hfill {\em August 2016 -- May 2020} \\ 
B.S. in Mathematics \& Computer Science \\
GPA: 3.79 \\
Relevant courses: Mathematical Statistics, Advanced Applied Statistics, Probability Theory, Mathematical Modeling, Optimization, Algorithms and Data Structures, Software Engineering, Operating Systems, Database Management Systems

{\bf DIS (study abroad)}, Copenhagen, Denmark \hfill {\em Fall 2019} \\
Relevant courses: Artificial Neural Networks and Deep Learning, Artificial Intelligence, Computational Analysis of Big Data

\end{rSection}


%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{McCormick Summer Research Scholar}{Summer 2019}{University of Puget Sound}{Tacoma, WA}
``\textit{Generating Artificial Mouse Ultrasonic Vocalizations using Generative Adversarial Networks}"
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Applied a complex Morlet wavelet transform to raw mouse vocalization recordings to produce visual representations in the form of scalograms.
\item Implemented a generative adversarial network model trained using NVIDIA's progressive training methodology and produced promising results for $16 \times 32$ and $32 \times 64$ resolution scalogram slices.
\end{itemize}
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Computer Science Assistant}{2018 -- 2019}{University of Puget Sound}{Tacoma, WA}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Assisted professors as a TA, grader, and afternoon tutor for Operating Systems, Introduction to Computer Science, Data Structures, and Architectures courses. 
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Mathematics Assistant}{2017 -- 2019}{University of Puget Sound}{Tacoma, WA}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Assisted professors as a grader for Introduction to Applied Statistics and Calculus I \& II courses.
\item Worked as an afternoon tutor for Linear Algebra, Multivariate Calculus, and Applied Statistics courses.
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IT Intern}{June -- August 2018}{First Choice Bancorp}{Cerritos, CA}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Designed and programmed scripts for Windows AD group policies as part of merger and acquisition process.
\item Assisted in migrating mail servers and transitioning mobile device management platforms for over 300 users and user groups as part of the m\&a.
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Research and Development Intern}{May -- July 2015}{NOVAtime Technology Inc.}{Diamond Bar, CA}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Developed a JavaScript visualization of a time clock for a simpler hierarchical overview. 
\item Researched and developed Korean language localization for the time clock interface.
\item Presented the projects before the company's Board of Directors and Executives.\end{itemize}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{Trump Tweets Analysis}{Fall 2019}{\href{https://github.com/wsjung/ANNADL_final}{github.com/wsjung/ANNADL\_final}}{}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Worked in a team of four to analyze patterns in Trump's tweets (@realDonaldTrump) to predict if from Android or iPhone device.
\item Designed neural network models and selected for best validation accuracy based on raw and balanced datasets using Keras and TensorFlow. 
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Un-bottling the data}{Fall 2019}{\href{https://github.com/wsjung/caobd_project}{github.com/wsjung/caobd\_project}}{}
\renewcommand{\labelitemi}{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Created interactive map visualizations for visual analysis of wine features.
\item Designed a LSTM network to analyze wine review descriptions to predict the associated wine's review score. 
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Loggregate}{Fall 2018}{\href{https://github.com/wsjung/loggregate}{github.com/wsjung/loggregate}}{Scrum master, DBA}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Led a team of four in developing a study group management platform implemented using the Laravel PHP web framework.
\item Defined a BCNF optimized SQLite database schema and populated it using a Python script which collected course information from the web
\end{itemize}
\end{rSubsection}


\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRACURRICULARS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Extracurricular University Service}

{\bf Chair}, \textit{University of Puget Sound ACM Student Chapter} \hfill {2017 -- 2019} \\
{\bf Secretary}, \textit{University of Puget Sound Mathematics Club} \hfill {2017 -- 2018} \\
{\bf Webmaster}, \textit{University of Puget Sound ACM Student Chapter} \hfill {2016 -- 2017}

\end{rSection}


%----------------------------------------------------------------------------------------
%	AWARDS AND HONORS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards and Honors}

{McCormick Scholar Award} \hfill {2019} \\
{Thomas and Hilda Jack Scholarship} \hfill {Fall 2019} \\
{McGill Family Scholarship} \hfill {Fall 2018, Spring 2019} \\
{Dean's List} \hfill {Spring 2019, Fall 2018, Fall 2017}

\end{rSection}


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java, Python, R, C, MATLAB, JavaScript, PHP \\
Libraries & TensorFlow, PyTorch, Numpy, Sklearn, Pandas, Git, Flask \\
Databases & SQLite \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	AFFILIATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Affiliations}
Association for Computing Machinery \\
Upsilon Pi Epsilon Honor Society
\end{rSection}


%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{References}
Available on request
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
